Modal Abstractions for Virtualizing Memory Addresses

### 2024-07-10 examples.tex
a pass over section 5

Realizing page-table directory walk amounts to calling \textsf{pte\_get\_next\_table} for each level as shown in Figure \ref{walkpgdir}. Since there is not much interesting piece additional to the specification we discuss for \textsf{pte\_get\_next\_table} in Section \ref{}, in Figure \ref{}, we present the expected specification after the calls made for each level entry. At each specification Line (X,..) in Figure \ref{}, we see the accumulation of virtual-pte pointsto resources returned from \textsf{pte\_get\_next\_tabel} for each level (L4-L1), and finally return L1 level entry that is needed by \textsf{walkpgdir} at Line X in Figure \ref{}. 

@@

>>>>

Realizing page-table directory walk amounts to calling \textsf{pte\_get\_next\_table} for each level as shown in Figure \ref{walkpgdir}. The special part of the specficication for a page table walk can be considered as accumulation of memory mappings for the page-table entries visited and frame addresses for page-tables. For example, Line 23-24 in Figure \ref{walkpgdir} shows the virtual-pointsto for a L3 page table and the virtual-page-table-entry-pointsto for an L4 entry. In the final post-condition, we expect the accumulation of these resources from each level -- $\textsf{R}_{\textsf{walk\_succ}}$ -- which allows us to construct the path to the L1 entry in the tree to insert a new page.  

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi\setminus\{\textsf{entry},\textsf{entry}_{\textsf{pfn}}\},m)  }_{\rtv}$
